Subjective Experience of Demands and Resources across O*NET Job Elements

### 2024-06-11 Submission.Rmd
small tweaks

>Hyp 3.b: Strain and burnout are differentially predicted by challenges and hindrances.

@@

d <- ggplot(bottomresource, aes(x=reorder(description,-sd), y=mean)) + geom_bar(stat="identity", color="blue", position=position_dodge()) + theme_bw() +
  scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 60, simplify = FALSE), paste, collapse="\n")) + xlab("") + ylab("Lack of Consensus as a Resource") + 
  geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.2, position=position_dodge(.9)) + coord_flip(ylim=c(1,5))

@@

e <- ggplot(bottomchallenge, aes(x=reorder(description,-sd), y=mean)) + geom_bar(stat="identity", color="yellow", position=position_dodge()) + theme_bw() +
  scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 60, simplify = FALSE), paste, collapse="\n")) + xlab("") + ylab("Lack of Consensus as a Challenge") + geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.2, position=position_dodge(.9)) + coord_flip(ylim=c(1,5))

@@

f <- ggplot(bottomhindrance, aes(x=reorder(description,-sd), y=mean)) + geom_bar(stat="identity", color="red", position=position_dodge()) + theme_bw() +
  scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 60, simplify = FALSE), paste, collapse="\n")) + xlab("") + ylab("Lack of Consensus as a Hindrance") + geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.2, position=position_dodge(.9)) + coord_flip(ylim=c(1,5))

@@

```{r combinegraphs2, fig.cap="Characteristics percieved most *DIS*similarly (largest standard deviations).", fig.height=10}

>>>>

>Hyp 3.b: Strain and burnout are differentially predicted by challenges and hindrances. **Take a look at significant difference between slope coefficients (b's) of, for example, challenge-->strain & hindrance-->strain**

@@

d <- ggplot(bottomresource, aes(x=reorder(description,-sd), y=mean)) + geom_bar(stat="identity", color="blue", position=position_dodge()) + theme_bw() +
  scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 60, simplify = FALSE), paste, collapse="\n")) + xlab("") + ylab("Lack of Consensus as a Resource") + 
  geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.2, position=position_dodge(.9)) + coord_flip(ylim=c(1,6))

@@

e <- ggplot(bottomchallenge, aes(x=reorder(description,-sd), y=mean)) + geom_bar(stat="identity", color="yellow", position=position_dodge()) + theme_bw() +
  scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 60, simplify = FALSE), paste, collapse="\n")) + xlab("") + ylab("Lack of Consensus as a Challenge") + geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.2, position=position_dodge(.9)) + coord_flip(ylim=c(1,6))

@@

f <- ggplot(bottomhindrance, aes(x=reorder(description,-sd), y=mean)) + geom_bar(stat="identity", color="red", position=position_dodge()) + theme_bw() +
  scale_x_discrete(labels = function(x) lapply(strwrap(x, width = 60, simplify = FALSE), paste, collapse="\n")) + xlab("") + ylab("Lack of Consensus as a Hindrance") + geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.2, position=position_dodge(.9)) + coord_flip(ylim=c(1,6))

@@

```{r combinegraphs2, fig.cap="Characteristics percieved most **dissimilarly** (largest standard deviations).", fig.height=10}

### 2024-06-11 Submission.tex
small tweaks

\begin{quote}
Hyp 3.b: Strain and burnout are differentially predicted by challenges and hindrances.
\end{quote}

@@

\begin{figure}
\centering
\includegraphics{Submission_files/figure-latex/combinegraphs2-1.pdf}
\caption{\label{fig:combinegraphs2}Characteristics percieved most \emph{DIS}similarly (largest standard deviations).}
\end{figure}

@@

Table \ref{tab:chal-resource-table} summarizes the results. Sum scores for the predictors were used here, and predictor variables were mean centered prior to running the following regressions. First exploring engagement, \(R^2\) = 0.15, Adj. \(R^2\) = 0.15 which represents a statistically significant effect, \(F(2, 565) = 10.68\), \(p < .001\). The inclusion of the interaction term in step two of the model contributed a significant addition to the model, \(\Delta R^2\) = 0.00, \(\Delta F\) (1, 564) = 5.82, and thus provides statistical support for the presence of moderation. The total model explained xx\% of the variance in engagement, \(F(3, 564) = 9.49\), \(p < .001\) Figure \ref{fig:chal-resource-int} illustrates the interaction. With low levels of resources, the relationship between challenges and engagement is relatively flat and engagement is comparatively low. With more resources, the relationship between challenges and engagement is negative, but engagement still remains higher with greater reported challenge when more resources are perceived.

@@

Next, challenge stressors and resources explained XX\% of the variance in stress, \(R^2\) = .xx. Adj. \(R^2\) = .xx, which represents a non-significant effect, \emph{F}(x, xx) = xx.xx, \emph{p} xxx. The inclusion of the interaction term in step two of the model did not add significantly to the model, \(\Delta R^2\) = .xx, \(\Delta F\)(xx, xx) = .xx, \emph{p} = xxx. The total model explained xx\% of the variance in stress, \(R^2\) = .xx. Adj. \(R^2\) = .xx, \emph{F}(x, xx) = xx.xx, \emph{p} \textless.xxx.

Finally, challenge stressors and resources explained XX\% of the variance in burnout, \(R^2\) = .xx. Adj. \(R^2\) = .xx, which represents a statistically significant effect, \emph{F}(x, xx) = xx.xx, \emph{p} xxx. The inclusion of the interaction term in step two of the model did not add significantly to the model, \(\Delta R^2\) = .xx, \(\Delta F\)(xx, xx) = .xx, \emph{p} = xxx. The total model explained xx\% of the variance in stress, \(R^2\) = .xx. Adj. \(R^2\) = .xx, \emph{F}(x, xx) = xx.xx, \emph{p} \textless.xxx. In sum, these findings do not provide support for the assertion that resources would moderate the relationships between challenge stressors and the outcomes of strain and burnout.

Sum scores for the predictors were used here, and predictor variables were mean centered prior to running the following regressions. First, hindrance stressors and resources explained XX\% of the variance in engagement, \(R^2\) = .xx. Adj. \(R^2\) = .xx, which represents a statistically significant effect, \emph{F}(x, xx) = xx.xx, \emph{p} xxx. The inclusion of the interaction term in step two of the model did not add significantly to the model, \(\Delta R^2\) = .xx, \(\Delta F\)(xx, xx) = .xx, \emph{p} = xxx. The total model explained xx\% of the variance in engagement, \(R^2\) = .xx. Adj. \(R^2\) = .xx, \emph{F}(x, xx) = xx.xx, \emph{p} \textless.xxx.

Next exploring stress, hindrance stressors and resources explained XX\% of the variance in stress, \(R^2\) = .xx. Adj. \(R^2\) = .xx, which represents a statistically significant effect, \emph{F}(x, xx) = xx.xx, \emph{p} xxx. The inclusion of the interaction term in step two of the model contributed a significant addition to the model, \(\Delta R^2\) = .xx, \(\Delta F\)(xx, xx) = .xx, \emph{p} = xx, and thus provides statistical support for the presence of moderation. The total model explained xx\% of the variance in stress, \(R^2\) = .xx. Adj. \(R^2\) = .xx, \emph{F}(x, xx) = xx.xx, \emph{p} \textless.xxx. See Figure \ref{fig:hind-resource-stress-int}. As expected, the relationship between hindrance stressors and strain becomes weaker as workers perceive more resources.

Similarly, hindrance stressors and resources explained XX\% of the variance in burnout, \(R^2\) = .xx. Adj. \(R^2\) = .xx, \emph{F}(x, xx) = xx.xx, \emph{p} xxx. The inclusion of the interaction term in step two of the model contributed a significant addition to the model, \(\Delta R^2\) = .xx, \(\Delta F\)(xx, xx) = .xx, \emph{p} = xx. The total model explained xx\% of the variance in burnout,\(R^2\) = .xx. Adj. \(R^2\) = .xx, \emph{F}(x, xx) = xx.xx, \emph{p} \textless.xxx. Again, see Figure \ref{fig:hind-resource-burn-int}. As expected, the relationship between hindrance stressors and burnout becomes weaker as workers perceive more resources.

>>>>

\begin{quote}
Hyp 3.b: Strain and burnout are differentially predicted by challenges and hindrances. \textbf{Take a look at significant difference between slope coefficients (b's) of, for example, challenge--\textgreater strain \& hindrance--\textgreater strain}
\end{quote}

@@

\begin{figure}
\centering
\includegraphics{Submission_files/figure-latex/combinegraphs2-1.pdf}
\caption{\label{fig:combinegraphs2}Characteristics percieved most \textbf{dissimilarly} (largest standard deviations).}
\end{figure}

@@

Table \ref{tab:chal-resource-table} summarizes the results. Sum scores for the predictors were used here, and predictor variables were mean centered prior to running the following regressions. First, challenges and resources explained a statistically significant amount of the variability in engagement, \(R^2\) = 0.15, Adj. \(R^2\) = 0.15, \(F(2, 565) = 50.09\), \(p < .001\). The inclusion of the interaction term in step two of the model contributed a significant addition to the model, \(F(3, 564) = 35.62\), \(p < .001\), \(\Delta R^2\) = 0.01, \(\Delta F\) (1, 564) = 5.82, and thus provides statistical support for the presence of moderation. Figure \ref{fig:chal-resource-int} illustrates the interaction. With low levels of resources, the relationship between challenges and engagement is relatively flat and engagement is comparatively low. With more resources, the relationship between challenges and engagement is negative, but engagement still remains higher with greater reported challenge when more resources are perceived.

Next, challenge stressors and resources did not explain a significant amount of the variance in stress, \(R^2\) = 0.01, Adj. \(R^2\) = 0, \(F(2, 565) = 1.67\), \(p = .189\). The inclusion of the interaction term in step two of the model did not contribute a significant addition to the model, \(F(3, 564) = 1.17\), \(p = .320\), \(\Delta R^2\) = 0.00, \(\Delta F\) (1, 564) = 0.17, and thus does not support the presence of moderation.

Finally, challenge stressors and resources explained a statsically significant amount of the variability in burnout, \(R^2\) = 0.04, Adj. \(R^2\) = 0.04, \(F(2, 565) = 1.67\), \(p = .189\). The inclusion of the interaction term in step two of the model did not contribute a significant addition to the model, \(F(3, 564) = 1.17\), \(p = .320\), \(\Delta R^2\) = 0.00, \(\Delta F\) (1, 564) = 2.25, and thus failing to provide statistical support for the presence of moderation. In sum, these findings do not provide support for the assertion that resources would moderate the relationships between challenge stressors and the outcomes of strain and burnout.

@@

Sum scores for the predictors were used here, and predictor variables were mean centered prior to running the following regressions. First, hindrance stressors and resources explained a statistically significant amount of the variability in engagement, \(R^2\) = 0.17, Adj. \(R^2\) = 0.16, \(F(2, 565) = 55.90\), \(p < .001\). The inclusion of the interaction term in step two of the model did not contribute a significant addition to the model, \(F(3, 564) = 37.25\), \(p < .001\), \(\Delta R^2\) = 0.00, \(\Delta F\) (1, 564) = 0.13. An interaction between hindrances and resources was not found.

Next exploring stress, hindrance stressors and resources explained a statistically significant amount of the variability in stress, \(R^2\) = 0.01, Adj. \(R^2\) = 0.01, \(F(2, 565) = 3.13\), \(p = .045\). The inclusion of the interaction term in step two of the model contributed a significant addition to the model, \(F(3, 564) = 6.89\), \(p < .001\), \(\Delta R^2\) = 0.03, \(\Delta F\) (1, 564) = 14.28, supporting the presence of a moderated effect. See Figure \ref{fig:hind-resource-stress-int}. As expected, the relationship between hindrance stressors and strain becomes weaker as workers perceive more resources.

Similarly, hindrance stressors and resources explained a statistically significant amount of the variability in burnout, \(R^2\) = 0.04, Adj. \(R^2\) = 0.03, \(F(2, 565) = 10.68\), \(p < .001\). The inclusion of the interaction term in step two of the model contributed a significant addition to the model, \(F(3, 564) = 9.49\), \(p < .001\), \(\Delta R^2\) = 0.01, \(\Delta F\) (1, 564) = 6.89, supporting the presence of a moderated effect. The total model explained xx\% of the variance in burnout,\(R^2\) = .xx. Adj. \(R^2\) = .xx, \emph{F}(x, xx) = xx.xx, \emph{p} \textless.xxx. Again, see Figure \ref{fig:hind-resource-burn-int}. As expected, the relationship between hindrance stressors and burnout becomes weaker as workers perceive more resources.
